A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2018-09-16 ionic_liquids.tex
Revision of the concentrated CO2 section

\begin{abstract}
In this paper, we calculate solvation free energies of several compounds in ionic liquids.
These free energies are used to compute properties such as Henry's law constants and activity coefficients, generally required to the design of environmentally sustainable processes.
It is known, for instance, that carbon dioxide from combustion is one of the main sources of anthropogenic greenhouse gases.
Recently, the propensity of ionic liquid \ce{[emim][B(CN)_4]} for the physisorption of \ce{CO_2} has been reported, which makes it a potential solvent for carbon capture.
In the present work, molecular dynamics simulations of the solvation of \ce{CO_2} in ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} are carried out both at infinite dilution and at high concentrations.
A systematic study is performed by comparing several force fields and assessing the efficacy of simplification measures such as rigid-body dynamics and pairwise electrostatics.
Our results confirm recent experimental observations that, for a given volume of solvent, lower pressure is required to absorb a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in other ionic liquids.
\end{abstract}

@@

There is no obvious explanation accounting for the enhanced solubility promoted by the presence of \ce{[B(CN)_4]^-}.
In this context, molecular simulation provides us with a powerful tool for studying solvation processes.
To the best of our knowledge, only one study in the literature reports computation of solvation free energy for \ce{CO_2} in \ce{[emim][B(CN)_4]} by molecular simulation \cite{Liu_2014_1}.
Nonetheless, the computed value is overestimated, as observed by deriving a Henry's law constant and comparing it to available experimental data.
Such scarcity motivated us to carry out the present investigation, in which we have evaluated different force fields for \ce{[emim][B(CN)_4]} proposed in the literature.
As we show here, it was possible to find a model that successfully reproduces the experimental value of the Henry constant of \ce{CO_2} in this IL.
For comparison, we analyzed the solvation of \ce{CO_2} not only in \ce{[emim][B(CN)_4]}, but also in \ce{[emim][NTf_2]}, both at infinite dilution and at high concentrations.
The simulations confirmed what is observed in experiments.
For \ce{[emim][B(CN)_4]}, a considerably lower pressure is required to dissolve the same amount of \ce{CO_2}, considering a given volume of solvent.
In addition, we also calculated infinite-dilution activity coefficients of other solutes in \ce{[emim][B(CN)_4]} and compared the results with experimental values recently reported in literature.
The solutes we considered were hexane, benzene, cyclohexane, ethanol, and water.

@@

In what follows, the subscripts ``s'' and ``IL'' refer to the solute and the solvent (ionic liquid), respectively.
For a liquid phase containing $N_\text{IL}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
\begin{equation}
\Delta G_\text{sim} \equiv R T \ln \frac{\Xi (N_s,N_\text{IL},P,T,\lambda = 1)}{\Xi (N_s,N_\text{IL},P,T,\lambda = 0)}, 
\end{equation}
where $\Xi$ denotes the isobaric-isothermal partition function and $R$ is the gas constant.
Shirts \textit{et al}. \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_\text{sim}$ to what is experimentally measured as the solvation free energy, namely
\begin{equation}
\label{eq:solvation free energy definition}
\Delta G_{\text{solv}} \equiv R \ln \left( \frac{P_s}{c_s R T} \right),
\end{equation}
where $P_s$ is the partial pressure of the solute in the gas phase and
$c_s$ is the molar concentration of the solute in the liquid phase.
Note that these quantities correspond to a phase equilibrium condition.
For obtaining the mentioned relation, the authors derived an expression for the chemical potential of the solute in the liquid phase ($\mu^l_s$) as a function of $\Delta G_\text{sim}$, which can be written as
\begin{equation}
\label{eq:solute chemical potential}
\mu^l_s = \mu^{ig}_s + \Delta G_\text{sim} - RT \ln \left( \frac{V^{\ast}}{V_1}\right) - RT \ln \left( \frac{P_s}{c_s R T} \right),
\end{equation}
where $\mu^{ig}_s$ is the chemical potential of the solute in an ideal gas at temperature $T$ and solute partial pressure $P_s$, while $V^{\ast}$ and $V_1$ are the mean volumes of liquid solutions specified by ($N_s-1$,$N_\text{IL}$,P,T) and ($N_s$,$N_\text{IL}$,P,T), respectively.
Note that $c_s = \frac{N_s}{N_A V_1}$.

@@

For the ILs of interest to the present investigation, high concentrations of \ce{CO_2} in the liquid phase are obtained at pressure values for which, in principle, the ideal gas assumption might no longer be valid.
In this case, we can compute the chemical potential of the solute in the real gas phase as
\begin{equation}
\label{eq:mu_gas_real}
\mu^{g}_s = \mu^{ig}_s + R T \ln \left(\frac{f^{g}_s}{P_s}\right),
\end{equation}
where $f^{g}_s$ is the fugacity of the solute in the gas phase.
Then, by considering a system at phase equilibrium ($\mu^{l}_s$ = $\mu^{g}_s$), it follows that
\begin{equation}
\label{eq:fgas_d}
f^{g}_s = \exp \left( \frac{\Delta G_\text{sim}}{R T} \right) +  c_s R T. 
\end{equation}

Three additional assumptions are made here. First, we assume that the gas phase is either pure solute (which is consistent with the ionic-liquid systems with which we compare our simulations) or can be approximated by an ideal solution. Second, we assume that the system pressure is moderate, so that a truncated virial equation is enough to represent the gas phase. In this case, Eq.~\eqref{eq:fgas_d} becomes
\begin{equation}
\label{eq:equilibrium pressure}
y_s \exp\left( \frac{B_s P}{R T} \right) P = \exp \left( \frac{\Delta G_\text{sim}}{R T} \right) +  c_s R T,
\end{equation}
where $y_s$ is the molar fraction of solute in the gas phase ($y_s \rightarrow 1$ for the systems we analyze here) and $B_s$ is the second virial coefficient of the solute.
In the case of \ce{CO_2}, we employ the correlation for $B_s$ developed by Holste \textit{et al}. \cite{Holste_1987}, which is
\begin{equation}
B_s = B_0 + \frac{B_1}{T} + \frac{B_2}{T^2},
\end{equation}
where $B_0 = 23.02991~\mathrm{\frac{cm^3}{mol}}$, $B_1 = -2455.297~\mathrm{\frac{K \cdot cm^3}{mol}}$, and $B_2 = -1.22675 \times 10^7~\mathrm{\frac{K^2 \cdot cm^3}{mol}}$.

@@

The gradual insertion/deletion of solutes involves scaling both the van der Waals (vdW) and the electrostatic intermolecular interactions.
To avoid numerical instabilities associated to the vdW scaling, it is usual to employ a soft-core potential with nonlinear coupling.
In this paper, we use the modified LJ potential proposed by Beutler \textit{et al}. \cite{Beutler_1994}, given by $V_\text{vdW}(r) = 4 \epsilon \lambda_\text{vdW} (s^{-2} - s^{-1})$, where $s = (r/\sigma)^6 + (1 - \lambda_\text{vdW})/2$.
The electrostatic interactions, on the other hand, can be linearly scaled by a coupling parameter $\lambda_\text{Coul}$ \cite{Naden_2015}, meaning that $V_\text{Coul}(r) = V_\text{Coul} V_\text{DSF}(r)$.
Furthermore, the vdW and Coulomb contributions to the free energy difference are taken into account separately.
That is,
\begin{equation}
\Delta G_\text{sim} = \Delta G_\text{vdW} + \Delta G_\text{Coul},
\end{equation}
where $\Delta G_\text{vdW}$ is computed by varying $\lambda_\text{vdW} \in [0,1]$ while keeping $\lambda_\text{Coul} = 0$, whereas $\Delta G_\text{Coul}$ is computed by varying $\lambda_\text{Coul} \in [0,1]$ while keeping $\lambda_\text{vdW} = 1$.
The sets of coupling parameter values we use here in all alchemical simulations are $\lambda_{\text{vdW}}$ = $\{0.0$, $0.05$, $0.1$, $0.2$, $0.25$, $0.3$, $0.35$, $0.4$, $0.45$, $0.5$, $0.6$, $0.7$, $0.8$, $0.9$, $1.0\}$ and $\lambda_{\text{Coul}}$ = $\{0.0$, $0.1$, $0.4$, $0.7$, $0.1\}$.

@@

Using the software TRAVIS \cite{Brehm_2011}, we obtained combined distribution functions (CDFs) of the dihedral angles formed in \ce{[emim]^+} by atoms C1-N2-C5-C6 and atoms C2-N2-C5-C6.
These angles will be referred to as $\psi_1$ and $\psi_2$, respectively.
In Fig.~\ref{fig:dihedrals_emim}, we show the CDFs obtained for all force fields employed here for \ce{[emim][B(CN)_4]}.
All CDFs shown in this section were generated from NPT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using our standard setup (i.e. flexible ions with PPPM Ewald electrostatics).
Initial inspection reveals that, in all cases, $\psi_1$ and $\psi_2$ populate regions of the diagrams around the two straight lines given by
\begin{equation}
\label{eq:dihedral angles}
\psi_2 = \begin{cases}
\psi_1 + 180^\circ & \text{if} \quad \psi_1 \leq 180^\circ \\
\psi_1 - 180^\circ & \text{if} \quad \psi_1 > 180^\circ
\end{cases},
\end{equation}
both corresponding to a coplanar structure formed by atoms C1, C2, N2, and C5.
There are two such lines in each diagram because atom C6 can be located on either side of the plan.
One can note in Fig.~\ref{fig:dihedrals_emim} that the CDF peaks, which indicate the most likely dihedral angle combinations, lie either precisely above these lines or very close to them.
The largest distortions from coplanarity occur for the Batista \textit{et al}. \cite{Batista_2015} model, as observed by the peak locations in Fig.~\ref{fig:dihedrals_emim}(b).
Despite this, all rigid bodies considered here for \ce{[emim]^+} are built in such a way that atoms C[1-5], H[1-3], and N[1-2] all lie in a single plan.
Therefore, for specifying the torsion of bond N2-C5 it is enough to set a value for $\psi_1$ and then compute $\psi_2$ by means of Eq.~\eqref{eq:dihedral angles}.
All other structural features (bond lengths, bending angles, and hydrogen-involving dihedrals) are taken from the minimum-energy structure obtained for each force field.

@@

\begin{table}
	\centering
	\caption{Thermodynamic conditions employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, based on the experimental observations of Refs.~ \citenum{Makino_2014} and \citenum{Schilderman_2007}.}
	\begin{tabular}{ccc}
		\hline\hline
		IL & \ce{[emim][B(CN)_4]}  & \ce{[emim][NTf_2]} \\
		\hline
%		model & Ref.~\citenum{Koller_2012} & Ref.~\citenum{Koddermann_2007} \\
		T  & 313.15 K & 312.13 K \\
		P  & 21 atm & 37 atm \\
		$x_s$ & 0.352 & 0.479 \\
		$m_s$ & 2.4 mol/kg & 2.35 mol/kg \\
		\hline\hline
		\label{table:solv} 
	\end{tabular}
\end{table}

We carried out expanded ensemble simulations of liquid solutions at the conditions of Table~\ref{table:solv}.
The model of Koller \textit{et al}. \cite{Koller_2012} was the one employed for \ce{[emim][B(CN)_4]}.
The computed solvation free energies for the systems \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][NTf_2]} were $-0.755 \pm 0.01 ~\mathrm{kcal/mol}$ and $-0.542 \pm 0.005~\mathrm{kcal/mol}$, respectively.
In Fig.~\ref{fig:pressure}, we present our predictions of the equilibrium pressure ($P$) obtained by solving Eq.~\eqref{eq:equilibrium pressure}, as well as the corresponding gas-phase fugacities of \ce{CO_2} ($f_s^g$) computed by Eq.~\eqref{eq:fgas_d}.
The dotted lines correspond to the experimental values (i.e. the ones used to simulate the liquid solutions).
First, the results make clear that assuming ideal gas would have been an oversimplification, specially in the case of \ce{[emim][NTf_2]}.
Second, the computed pressures did not depart considerably from the specified values, meaning that our results sustain the experimental observation that $P$ is considerably lower for the system \ce{CO_2}+\ce{[emim][B(CN)_4]} than for the system \ce{CO_2}+\ce{[emim][NTf_2]}.
In addition, we see that in this case the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).
%However, since we simulated a different number of \ce{CO_2}, we cannot draw any definite conclusion regarding the presence of stronger interactions with \ce{[emim][B(CN)_4]}, which could explain the higher solubility.

>>>>

\begin{abstract}
In this paper, we calculate solvation free energies of several compounds in ionic liquids.
These free energies are used to compute properties such as Henry's law constants and activity coefficients, generally required in the design of environmentally sustainable processes.
It is known, for instance, that carbon dioxide from combustion is one of the main sources of anthropogenic greenhouse gases.
Recently, the propensity of the ionic liquid \ce{[emim][B(CN)_4]} for the physisorption of \ce{CO_2} has been reported, which makes it a potential solvent for carbon capture.
In the present work, molecular dynamics simulations of the solvation of \ce{CO_2} in ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} are carried out both at infinite dilution and at high concentrations.
A systematic study is performed by comparing several force fields and assessing the efficacy of simplification measures such as rigid-body dynamics and pairwise electrostatics.
Our results confirm recent experimental observations that, for a given volume of solvent, lower pressure is required to absorb a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in other ionic liquids.
\end{abstract}

@@

There is no obvious explanation accounting for the enhanced solubility promoted by the presence of \ce{[B(CN)_4]^-}.
In this context, molecular simulation provides us with a powerful tool for studying solvation processes.
To the best of our knowledge, only one study in the literature reports computation of solvation free energy for \ce{CO_2} in \ce{[emim][B(CN)_4]} by molecular simulation \cite{Liu_2014_1}.
Nonetheless, the computed value is overestimated, as observed by deriving a Henry's law constant and comparing it to available experimental data.
Such scarcity motivated us to carry out the present investigation, in which we have evaluated different force fields for \ce{[emim][B(CN)_4]} proposed in the literature.
As we show here, it was possible to find a model that successfully reproduces the experimental value of the Henry constant of \ce{CO_2} in this IL.
For comparison, we analyzed the solvation of \ce{CO_2} not only in \ce{[emim][B(CN)_4]}, but also in \ce{[emim][NTf_2]}, both at infinite dilution and at high concentrations.
The simulations confirmed what is observed in experiments.
For \ce{[emim][B(CN)_4]}, a considerably lower pressure is required to dissolve the same amount of \ce{CO_2}, considering a given mass of solvent.
In addition, we also calculated infinite-dilution activity coefficients of other solutes in \ce{[emim][B(CN)_4]} and compared the results with experimental values recently reported in literature.
The solutes we considered were hexane, benzene, cyclohexane, ethanol, and water.

@@

In what follows, the subscripts ``s'' and ``IL'' refer to the solute and the solvent (ionic liquid), respectively.
For a liquid phase containing $N_\text{IL}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
\begin{equation}
\Delta G_\text{sim} \equiv R T \ln \frac{\Xi (N_s,N_\text{IL},P,T,\lambda = 1)}{\Xi (N_s,N_\text{IL},P,T,\lambda = 0)}, 
\end{equation}
where $\Xi$ denotes the isobaric-isothermal partition function and $R$ is the gas constant.
Shirts \textit{et al}. \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_\text{sim}$ to what is experimentally measured as the solvation free energy, namely
\begin{equation}
\label{eq:solvation free energy definition}
\Delta G_{\text{solv}} \equiv R T \ln \left( \frac{P_s}{c_s R T} \right),
\end{equation}
where $P_s$ is the partial pressure of the solute in the gas phase and
$c_s$ is the molar concentration of the solute in the liquid phase.
Note that these quantities correspond to a phase equilibrium condition.
For obtaining the mentioned relation, the authors derived an expression for the chemical potential of the solute in the liquid phase ($\mu^l_s$) as a function of $\Delta G_\text{sim}$, which can be written as
\begin{equation}
\label{eq:solute chemical potential}
\mu^l_s = \mu^{ig}_s + \Delta G_\text{sim} - RT \ln \left( \frac{V^{\ast}}{V_1}\right) - RT \ln \left( \frac{P_s}{c_s R T} \right),
\end{equation}
where $\mu^{ig}_s$ is the chemical potential of the solute in an ideal gas at temperature $T$ and solute partial pressure $P_s$, while $V^{\ast}$ and $V_1$ are the mean volumes of liquid solutions specified by ($N_s-1$,$N_\text{IL}$,P,T) and ($N_s$,$N_\text{IL}$,P,T), respectively.
Note that $c_s = \frac{N_s}{N_A V_1}$, where $N_A$ is the Avogadro number.

@@

For the ILs of interest to the present investigation, high concentrations of \ce{CO_2} in the liquid phase are obtained at pressure values for which, in principle, the ideal gas assumption might no longer be valid.
In this case, we can compute the chemical potential of the solute in the real gas phase as
\begin{equation}
\label{eq:mu_gas_real}
\mu^{g}_s = \mu^{ig}_s + R T \ln \left(\frac{f^{g}_s}{P_s}\right),
\end{equation}
where $f^{g}_s$ is the fugacity of the solute in the gas phase.
Then, by considering a system at phase equilibrium ($\mu^{l}_s$ = $\mu^{g}_s$), it follows that
\begin{equation}
\label{eq:fgas_d}
f^{g}_s = c_s R T \exp \left( \frac{\Delta G_\text{sim}}{R T} \right). 
\end{equation}

Three additional assumptions are made here. First, we assume that the gas phase is either pure solute (which is consistent with the ionic-liquid systems with which we compare our simulations) or can be approximated by an ideal solution. Second, we assume that the system pressure is moderate, so that a truncated virial equation is enough to represent the gas phase. In this case, Eq.~\eqref{eq:fgas_d} becomes
\begin{equation}
\label{eq:equilibrium pressure}
y_s \exp\left( \frac{B_s P}{R T} \right) P = c_s R T \exp \left( \frac{\Delta G_\text{sim}}{R T} \right),
\end{equation}
where $y_s$ is the molar fraction of solute in the gas phase ($y_s \rightarrow 1$ for the systems we analyze here) and $B_s$ is the second virial coefficient of the solute.
In the case of \ce{CO_2}, we employ the correlation for $B_s$ developed by Holste \textit{et al}. \cite{Holste_1987}, which is
\begin{equation}
B_s = B_0 + \frac{B_1}{T} + \frac{B_2}{T^2},
\end{equation}
where $B_0 = 23.02991~\mathrm{\frac{cm^3}{mol}}$, $B_1 = -2455.297~\mathrm{\frac{K \cdot cm^3}{mol}}$, and $B_2 = -1.22675 \times 10^7~\mathrm{\frac{K^2 \cdot cm^3}{mol}}$.

@@

The gradual insertion/deletion of solutes involves scaling both the van der Waals (vdW) and the electrostatic intermolecular interactions.
To avoid numerical instabilities associated to the vdW scaling, it is usual to employ a soft-core potential with nonlinear coupling.
In this paper, we use the modified LJ potential proposed by Beutler \textit{et al}. \cite{Beutler_1994}, given by $V_\text{vdW}(r) = 4 \epsilon \lambda_\text{vdW} (s^{-2} - s^{-1})$, where $s = (r/\sigma)^6 + (1 - \lambda_\text{vdW})/2$.
The electrostatic interactions, on the other hand, can be linearly scaled by a coupling parameter $\lambda_\text{Coul}$ \cite{Naden_2015}, meaning that $V_\text{Coul}(r) = \lambda_\text{Coul} V_\text{DSF}(r)$.
Furthermore, the vdW and Coulomb contributions to the free energy difference are taken into account separately.
That is,
\begin{equation}
\Delta G_\text{sim} = \Delta G_\text{vdW} + \Delta G_\text{Coul},
\end{equation}
where $\Delta G_\text{vdW}$ is computed by varying $\lambda_\text{vdW} \in [0,1]$ while keeping $\lambda_\text{Coul} = 0$, whereas $\Delta G_\text{Coul}$ is computed by varying $\lambda_\text{Coul} \in [0,1]$ while keeping $\lambda_\text{vdW} = 1$.
The sets of coupling parameter values we use here in all alchemical simulations are $\lambda_{\text{vdW}}$ = $\{0.0$, $0.05$, $0.1$, $0.2$, $0.25$, $0.3$, $0.35$, $0.4$, $0.45$, $0.5$, $0.6$, $0.7$, $0.8$, $0.9$, $1.0\}$ and $\lambda_{\text{Coul}}$ = $\{0.0$, $0.1$, $0.4$, $0.7$, $0.1\}$.

@@

Using the software TRAVIS \cite{Brehm_2011}, we obtained combined distribution functions (CDFs) of the dihedral angles formed in \ce{[emim]^+} by atoms C1-N2-C5-C6 and atoms C2-N2-C5-C6.
These angles will be referred to as $\psi_1$ and $\psi_2$, respectively.
In Fig.~\ref{fig:dihedrals_emim}, we show the CDFs obtained for all force fields employed here for \ce{[emim][B(CN)_4]}.
All CDFs shown in this section were generated from NPT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using our standard setup (i.e. flexible ions with PPPM Ewald electrostatics).
Initial inspection reveals that, in all cases, $\psi_1$ and $\psi_2$ populate regions of the diagrams around the two straight lines given by
\begin{equation}
\label{eq:dihedral angles}
\psi_2 = \begin{cases}
\psi_1 + 180^\circ & \text{if} \quad \psi_1 \leq 180^\circ \\
\psi_1 - 180^\circ & \text{if} \quad \psi_1 > 180^\circ
\end{cases},
\end{equation}
both corresponding to a coplanar structure formed by atoms C1, C2, N2, and C5.
%There are two such lines in each diagram because atom C6 can be located on either side of the plane.
One can note in Fig.~\ref{fig:dihedrals_emim} that the CDF peaks, which indicate the most likely dihedral angle combinations, lie either precisely above these lines or very close to them.
The largest distortions from coplanarity occur for the Batista \textit{et al}. \cite{Batista_2015} model, as observed by the peak locations in Fig.~\ref{fig:dihedrals_emim}(b).
Despite this, all rigid bodies considered here for \ce{[emim]^+} are built in such a way that atoms C[1-5], H[1-3], and N[1-2] all lie in a single plane.
Therefore, for specifying the torsion of bond N2-C5 it is enough to set a value for $\psi_1$ and then compute $\psi_2$ by means of Eq.~\eqref{eq:dihedral angles}.
All other structural features (bond lengths, bending angles, and hydrogen-involving dihedrals) are taken from the minimum-energy structure obtained for each force field.

@@

\begin{table}
	\centering
	\caption{Thermodynamic conditions, based on the experimental observations of Refs.~\citenum{Makino_2014} and \citenum{Schilderman_2007}, employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, as well as the results obtained via expanded ensemble simulations.}
	\begin{tabular}{ccc}
		\hline\hline
		IL & \ce{[emim][B(CN)_4]}  & \ce{[emim][NTf_2]} \\
		\hline
%		model & Ref.~\citenum{Koller_2012} & Ref.~\citenum{Koddermann_2007} \\
		\multicolumn{3}{c}{Specification} \\
		$T$  & $313.15~\mathrm{K}$ & $312.13~\mathrm{K}$ \\
		$P$  & $21~\mathrm{atm}$ & $37~\mathrm{atm}$ \\
		$x_s$ & $0.352$ & $0.479$ \\
		$m_s$ & $2.4~\mathrm{mol/kg}$ & $2.35~\mathrm{mol/kg}$ \\
		\hline
		\multicolumn{3}{c}{Simulation Result} \\
		$c_s$ & $3.04~\mathrm{mol/dm^3}$ & $2.22~\mathrm{mol/dm^3}$ \\ 
		$\Delta G_\text{sim}$ & $-0.755~\mathrm{kcal/mol}$ & $-0.542~\mathrm{kcal/mol}$ \\
		$P$ & $18.3~\mathrm{atm}$ & $38.4~\mathrm{atm}$ \\
		\hline\hline
		\label{table:solv} 
	\end{tabular}
\end{table}

We carried out expanded ensemble simulations of liquid solutions at the conditions of Table~\ref{table:solv}.
The model of Koller \textit{et al}. \cite{Koller_2012} was the one employed for simulating \ce{[emim][B(CN)_4]}.
The computed solvation free energies for the systems \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][NTf_2]} were $-0.755 \pm 0.009 ~\mathrm{kcal/mol}$ and $-0.542 \pm 0.005~\mathrm{kcal/mol}$, respectively.
In Fig.~\ref{fig:pressure}, we present our predictions of the equilibrium pressure ($P$) obtained by solving Eq.~\eqref{eq:equilibrium pressure}, as well as the corresponding gas-phase fugacities of \ce{CO_2} ($f_s^g$) computed by Eq.~\eqref{eq:fgas_d}.
The dotted lines correspond to the experimental values (i.e. those used to simulate the liquid solutions).
First, the results make clear that assuming ideal gas ($P = f_s^g$) would have been an oversimplification, specially in the case of \ce{[emim][NTf_2]}.
Second, and most importantly, the computed pressures did not depart considerably from the specified values, meaning that our results sustain the experimental observations.
Therefore, as the pressure required to reach the same equilibrium molal concentration of \ce{CO_2} in the liquid phase is smaller for \ce{[emim][B(CN)_4]} than for \ce{[emim][NTf_2]}, our results confirm that the former is a better solvent than the latter.
This confirmation was possible by simulating a purely physical absorption, without considering any quantum effect.
